Combinatorics of the geometry of Wilson loop diagrams II: Grassmann necklaces, dimensions, and denominators

### 2020-10-18 GWLDCII.tex
addressed paper 2 report Y

@@

@@

Marcott in \cite{WLDdim} gives a different proof of the $3|\cP|$-dimensionality of $M(W)$ which is geometric and more elegant, but it is not easy to track the effect of a particular propagator.

>>>>

It is worth noting at this point that the combinatorics of the Wilson loop diagrams are different from the combinatorics of the Amplituhedron, just as the the volume forms associated to the BCFW diagrams are different from those associated to the Wilson Loop diagrams. For instance, the BCFW are most readily related to the geometry of a postive Grassmanian via plabic graphs. Meanwhile, the Wilson loop diagrams correspond to matrices with variable valued entries (see section \ref{section WLD background}) and Grassmann Necklaces (see Algorithm \ref{alg:put GN on WLD}).  These two combinatorial representations of the positive Grassmannians have different strengths and weaknesses, and it is not possible to give a one to one translation of the combinatorial tools used for the Amplituhedron and BCFW diagrams, and the combinatorial tools used for the Wilson loop diagrams, associated matrices and Grassmann Necklaces. For instance, square moves and merge-expand moves give different graphical representations of the same positroid cell. There is no equivalent diagramatical equivalence for Wilson loop diagrams, though it has been shown (see \cite{wilsonloop, GWLDCI}) that certain classes of diagrams parametrize the same positroid cells. On the other hand, in order to get a parametrization of the associated positroid cell from the plabic graphs, one must assign weights to the vertices and used them to compute Pl\"{u}cker coordinates \cite[Section 11]{Postnikov}, while the Wilson loop diagrams \emph{are} a parametrization of the associated positroid. I.e. one can compute the Pl\"{u}cker coordinates directed from the associated matrices.  \sanote{This para is in answer to 1 and 4 of report Y. Should it be moved (in a modified form) to the begining of section 3? Should it be in both places?}

@@

A reader interested in studying these integrals further is invited to read \cite{casestudy, HeslopStewart, Amplituhedronsquared} in order to understand the connection to the scattering amplitude of $N=4$ SYM theory, the cancelation of spurious poles of specific instances of these integrals as well as explicit amplitude calculations. \sanote{I don't think I need to say more for point 2 of report Y?}

@@

Marcott in \cite{WLDdim} gives a different proof of the $3|\cP|$-dimensionality of $M(W)$ which is geometric and more elegant, but it is not easy to track the effect of a particular propagator.  It is worth noting that while the Amplituhedon is also defined by a projection of a set of $4|\cP|$ dimensional positroid cells, there is no evidence to suggest that the $3|\cP|$ dimensional cells of $\Gr(|\cP|, n)$ defiining the Wilson loop diagrams are related to the $4|\cP|$ dimensional cells defining the Amplituhedron.  \sanote{This para adresses point 3 of report Y. Should there be a similar paragraph in the intro? Should it be moved?}
